% This file contains definitions of various fields used
% in various places throughout the thesis (in the title
% pages mostly). Whatever isn't define here has some
% default (and usually irrelevant) text.

\authorEnglish{Christoph Velling}
\authorHebrew{כריסטוף פלינג}

%\titleEnglish{Improved methods \\ for the cultivation of lettuce \\ on the coastal plane}
%\titleHebrew{שיטות משופרות \\ לגידול חסה במישור החוף}

\disciplineEnglish{Biology}
\disciplineHebrew{מדעי המחשב}

\supervisionEnglish{This research was carried out under the supervision of Prof.~Roy Kishony, in the Faculty of Computer Science.}
\supervisionHebrew{המחקר בוצע בהנחייתו של פרופסור אישחשוב עצמוני, בפקולטה למדעי המחשב.}

\GregorianDateEnglish{September 2025}
\GregorianDateHebrew{ינואר \textenglish{2025}}
\JewishDateEnglish{Tishrei 5786}
\JewishDateHebrew{תשרי התשפ"ו}

%\financialAcknowledgementEnglish{The Technion's funding of this research is hereby acknowledged.}
%\financialAcknowledgementHebrew{הכרת תודה מסורה לטכניון על מימון מחקר זה.}

\publicationInfoEnglish{%
%Remove this parenthesized note and the line following it!
(The grad school guidelines now require that you mention the following regarding publications of your thesis work; but of course, remove this parenthesized note...; you will find the note in the \texttt{thesis-fields.tex} file. The entries for the publication list are BiBTeX bibliography entries, separate from those in the main bibliography: You must place them in \texttt{front/pubinfo.bib}; make sure their labels are distinct from entries in the main bibliography; and order them in the order in which you want them to appear --- they will not be sorted. Note also that the document may need to be processed several times before the list of publications actually appears)

Some results in this thesis have been published as articles by the author and research collaborators in conferences and journals during the course of the author's doctoral research period, the most up-to-date versions of which being:

\butcheredbibliography{front/pubinfo.bib}
}
\ethicsStatementEnglish{%
The research underlying this thesis was conducted honestly, in accordance with the ethical standards customary in academia. This applies, in particular, to the collection, processing and presentation of data, the description of and comparison with previous research work, etc. 
Also, the report on research activities and findings in this work is thorough and honest in accordance with the aforementioned standards.

}

\publicationInfoHebrew{%
(התייחסות לפרסומים, שמופיעה להלן, הינה הכרחית לפי תקנות ביה"ס ללימודי מוסמכים; כמובן שיש למחוק את ההערה הזו שבסוגריים... תוכן זה נמצאה בקובץ \textenglish{\texttt{thesis-fields.tex}}. הרשומות לצורך רשימת הפרסומים הינן רשומות \textenglish{BibTeX}, נפרדות מן הרשומות בביבליוגרפיה העיקרית של המסמך: עליך לשים אותן בקובץ \textenglish{\texttt{front/pubinfo.bib}}; הקפיד/י שהתוויות שלהם יהיו שונות מתוויות הרשומות בביליוגרפיה העיקרית. רשום/י אותם בסדר בהם תרצה/י שיופיעו ברשימה --- שכן הן לא ימוינו. כן שים/י לב שייתכן שיהיה צורך להדר את המסמך פעם או פעמיים נוספות עד שהרשימה אכן תופיע כראוי.)

חלק מן התוצאות בחיבור זה פורסמו כמאמרים מאת המחבר ושותפיו למחקר בכנסים ובכתבי-עת במהלך תקופת מחקר הדוקטורט של המחבר, אשר גרסאותיהם העדכניות ביותר הינן:%

\begin{otherlanguage}{english}%
\butcheredbibliography{front/pubinfo.bib}
\end{otherlanguage}%
}

\ethicsStatementHebrew{%
המחקר שבבסיס חיבור זה נערך כולו ביושר, ולפי אמות המידה האתיות המקובלות באקדמיה. בפרט אמורים הדברים בפעילויות איסוף הנתונים, עיבודם והצגתם, התייחסות והשוואה למחקרים קודמים וכו', ככל שהיוו חלק מן המחקר. כמו כן, הדיווח על המחקר ותוצאותיו בחיבור זה הוא מלא וישר, לפי אותן אמות מידה.

}
\addbibresource{back/general.bib}
\addbibresource{back/Paperpile - _PhD_thesis_final_bib - Sep 21.bib}
% \thesisbibstyle{trad-alpha}
